\documentclass{article}

\usepackage{multicol}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[landscape,margin=0.25in]{geometry}
\usepackage{tikz}
\usepackage[mirror]{crop}
\usepackage{everypage}
\AddEverypageHook{\special{pdf: put @thispage <</Rotate -90>>}}

\begin{document}

\pagestyle{empty}

\newfontfamily\swfill{SuttonSignWritingFill.ttf}
\newfontfamily\swline{SuttonSignWritingLine.ttf}

\setlength{\parindent}{0pt}
\setlength{\columnseprule}{1pt}
\newcommand{\signsize}{10}
\newcommand{\enubox}[1]{\reflectbox{\rotatebox[origin=r]{-90}{\begin{minipage}{0.08\textwidth}\begin{center}#1\end{center}\end{minipage}}}}

\begin{center}
\renewcommand{\signsize}{20}
\enubox{\Large\bf 2 John}
\raisebox{20pt}{B508x515S10e00493x485} \raisebox{20pt}{B519x519S19220498x500S2a20c481x482} \raisebox{20pt}{B508x508S17620492x492} \raisebox{20pt}{B515x508S11502485x493} \raisebox{20pt}{B511x513S11920490x487} 
\end{center}

\renewcommand{\signsize}{10}

\begin{multicols}{2}


\begin{center}
\enubox{\bf Chapter 1}
M517x530S15a48484x471S16d40499x475S22b04501x500 M508x515S10000493x485 
\end{center}


\enubox{1 The elder unto the elect lady and her children, whom I love in the truth; and not I only, but also all they that have known the truth;}

\enubox{2 For the truth's sake, which dwelleth in us, and shall be with us for ever.}

\enubox{3 Grace be with you, mercy, and peace, from God the Father, and from the Lord Jesus Christ, the Son of the Father, in truth and love.}

\enubox{4 I rejoiced greatly that I found of thy children walking in truth, as we have received a commandment from the Father.}

\enubox{5 And now I beseech thee, lady, not as though I wrote a new commandment unto thee, but that which we had from the beginning, that we love one another.}

\enubox{6 And this is love, that we walk after his commandments. This is the commandment, That, as ye have heard from the beginning, ye should walk in it.}

\enubox{7 For many deceivers are entered into the world, who confess not that Jesus Christ is come in the flesh. This is a deceiver and an antichrist.}

\enubox{8 Look to yourselves, that we lose not those things which we have wrought, but that we receive a full reward.}

\enubox{9 Whosoever transgresseth, and abideth not in the doctrine of Christ, hath not God. He that abideth in the doctrine of Christ, he hath both the Father and the Son.}

\enubox{10 If there come any unto you, and bring not this doctrine, receive him not into your house, neither bid him God speed:}

\enubox{11 For he that biddeth him God speed is partaker of his evil deeds.}

\enubox{12 Having many things to write unto you, I would not write with paper and ink: but I trust to come unto you, and speak face to face, that our joy may be full.}

\enubox{13 The children of thy elect sister greet thee. Amen.}

\end{multicols}

\end{document}

