\documentclass{article}

\usepackage{multicol}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[landscape,margin=0.25in]{geometry}
\usepackage{tikz}
\usepackage[mirror]{crop}
\usepackage{everypage}
\AddEverypageHook{\special{pdf: put @thispage <</Rotate -90>>}}

\begin{document}

\pagestyle{empty}

\newfontfamily\swfill{SuttonSignWritingFill.ttf}
\newfontfamily\swline{SuttonSignWritingLine.ttf}

\setlength{\parindent}{0pt}
\setlength{\columnseprule}{1pt}
\newcommand{\signsize}{10}
\newcommand{\enubox}[1]{\reflectbox{\rotatebox[origin=r]{-90}{\begin{minipage}{0.08\textwidth}\begin{center}#1\end{center}\end{minipage}}}}

\begin{center}
\renewcommand{\signsize}{20}
\enubox{\Large\bf 3 John}
\raisebox{20pt}{B512x515S11e20489x485} \raisebox{20pt}{B519x519S19220498x500S2a20c481x482} \raisebox{20pt}{B508x508S17620492x492} \raisebox{20pt}{B515x508S11502485x493} \raisebox{20pt}{B511x513S11920490x487} 
\end{center}

\renewcommand{\signsize}{10}

\begin{multicols}{2}


\begin{center}
\enubox{\bf Chapter 1}
M517x530S15a48484x471S16d40499x475S22b04501x500 M508x515S10000493x485 
\end{center}


\enubox{1 The elder unto the wellbeloved Gaius, whom I love in the truth.}

\enubox{2 Beloved, I wish above all things that thou mayest prosper and be in health, even as thy soul prospereth.}

\enubox{3 For I rejoiced greatly, when the brethren came and testified of the truth that is in thee, even as thou walkest in the truth.}

\enubox{4 I have no greater joy than to hear that my children walk in truth.}

\enubox{5 Beloved, thou doest faithfully whatsoever thou doest to the brethren, and to strangers;}

\enubox{6 Which have borne witness of thy charity before the church: whom if thou bring forward on their journey after a godly sort, thou shalt do well:}

\enubox{7 Because that for his name's sake they went forth, taking nothing of the Gentiles.}

\enubox{8 We therefore ought to receive such, that we might be fellowhelpers to the truth.}

\enubox{9 I wrote unto the church: but Diotrephes, who loveth to have the preeminence among them, receiveth us not.}

\enubox{10 Wherefore, if I come, I will remember his deeds which he doeth, prating against us with malicious words: and not content therewith, neither doth he himself receive the brethren, and forbiddeth them that would, and casteth them out of the church.}

\enubox{11 Beloved, follow not that which is evil, but that which is good. He that doeth good is of God: but he that doeth evil hath not seen God.}

\enubox{12 Demetrius hath good report of all men, and of the truth itself: yea, and we also bear record; and ye know that our record is true.}

\enubox{13 I had many things to write, but I will not with ink and pen write unto thee:}

\enubox{14 But I trust I shall shortly see thee, and we shall speak face to face. Peace be to thee. Our friends salute thee. Greet the friends by name.}

\end{multicols}

\end{document}

